Combined effects of protein expression variance and correlation on multicomponent systems

### 2020-03-11 Manuscript/Manuscript.Rmd
.

```{r figure_2, echo=FALSE, fig.height=7, fig.width=6, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_2}
p1 <- ggplot(allGroups, aes(x = normVar, fill = interval)) + 
  geom_histogram(bins = 50) + theme_minimal() +
  #scale_fill_viridis_d()
  scale_fill_manual(values = c("#d53e4f","#3288bd","grey")) +
  xlab("Normalized Variation") + ylab("Number") +
  theme(legend.position = "none")

@@

#p1 + p2 + p3 + plot_annotation(tag_levels = "A")

@@

@@

```{r figure_3, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_3}
library(circlize)

>>>>

```{r figure_2, echo=FALSE, fig.height=7, fig.width=6, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_2}
p1 <- ggplot(allGroups, aes(x = normVar, fill = interval)) + 
  geom_histogram(data = filter(allGroups, interval == "mid"),bins = 50) + 
  geom_histogram(data = filter(allGroups, interval == "low"),bins = 50) + 
  geom_histogram(data = filter(allGroups, interval == "high"),bins = 50) + 
  theme_minimal() +
  scale_fill_manual(values = c("#d53e4f","#3288bd","grey")) +
  xlab("Normalized Variation") + ylab("Number") +
  theme(legend.position = "none")

@@

@@

```{r figure_3, echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_3}
plots <- 1:4
for(i in 1:length(plots)){
  assign(paste0("p",plots[i]), cor_rug_plot(interesting_groups_low[i], "#3288bd"))
}

plots <- 5:8
for(i in 1:length(plots)){
  assign(paste0("p",plots[i]), cor_rug_plot(interesting_groups_high[i], "#d53e4f"))
}

left <- p1 + p2 + p3 + p4 + plot_layout(nrow = 1)

right <- p5 + p6 + p7 + p8 + plot_layout(nrow = 1)

wrap_plots(left, right) + plot_annotation(tag_levels = "A") + plot_layout(nrow = 2)

fig_legend_3 <- c("Density plots of correlation coefficients select protein groups color coded by low (blue) and high (red) normalized protein variance, with the distribution of all measured correlation coefficients colored in grey (rug plot to show the measured correlations coefficents shown on plot). Below each density plot is a box plot.")
```

@@

```{r figure_4, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_3}
library(circlize)
